Plots for Latent Hawkes Paper

### 2021-07-06 output_scripts/Paper_Plots.Rmd
just general tidying

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.path = "paper_figure/",
  dev = "png", fig.height = 4.5, fig.width = 7,
  warning = FALSE
)

@@

```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE, eval=revision_plots}
# current_cohort <- 5

@@

ks.stat.matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
n_matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
Lambda_matrix <- matrix(list(), nrow = mice_number, ncol = mice_number)
for (k in 1:mice_number) {
  for (l in c(1:mice_number)[-k]) {
    i <- expert_rank_10[[current_cohort]][k]
    j <- expert_rank_10[[current_cohort]][l]
    pair <- which(unique_pairs_df$initiator == i & 
                    unique_pairs_df$recipient == j)
    if (length(pair) > 0) {
      param_mean <- list(
        lambda0 = mean(sim_cohort_hp$lambda0),
        alpha = model1_fn$alpha.fun(
          f_est[i],
          f_est[j],
          eta1_mean,
          eta2_mean,
          eta3_mean
        ),
        beta = mean(sim_cohort_hp$beta)
      )
      current_window_vec <- unique_pairs_df$observe[[pair]]
      all_Lambda <- numeric(0)
      for (cur in c(1:length(current_window_vec))) { ## check length > 2
        cur_win <- current_window_vec[cur]
        current_event_time <- return_df[return_df$initiator == i &
          return_df$recipient == j &
          return_df$observe.id == cur_win, "event.times"][[1]]
        current_obs_time <- return_df[return_df$initiator == i &
          return_df$recipient == j &
          return_df$observe.id == cur_win, "observe.time"]
        Lambda_vec <- uniHawkesCompensator(
          object = param_mean,
          events = c(
            current_event_time,
            current_obs_time
          )
        )
        all_Lambda <- c(all_Lambda, Lambda_vec)
        n_matrix[i, j] <- n_matrix[i, j] + length(current_event_time)
      }
      if (length(all_Lambda) > 0) {
        ks.stat.matrix[i, j] <- ks.test(all_Lambda, "pexp",
          rate = 1 / mean(all_Lambda)
        )$statistic
        Lambda_matrix[i, j][[1]] <- all_Lambda
      }
    }
  }
}
#
# png(paste(plot_path,
#           "/diagonsis_model1_",
#           cohort_names[current_cohort],
#           ".png",
#           sep = ''),
#     width=480,height=480)
# -------------- KS plot (stat)
col.vec <- cRamp(as.vector(ks.stat.matrix))
# need to do some sort of transformation between these here
vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix))))
# order(as.vector(ks.stat.matrix),method = "")

@@

mtext(
  text = expert_rank_10[[current_cohort]],
  side = 1, line = 1.8, outer = TRUE, cex = 1.8,
  at = 1 / 14 * c(1:12) - 1 / 22
)
mtext(
  text = expert_rank_10[[current_cohort]],
  side = 2, line = 0.5, outer = TRUE, cex = 1.8,
  at = 1 / 12 * c(12:1) - 1 / 20, las = 2
)
mtext(
  text = "(b)", side = 3, line = 1.4, outer = TRUE,
  cex = 2.2,
  at = 0.45, font = 2
)
# dev.off()
```

@@

```{r fig-3a-baseline-rate, eval=revision_plots}
# current_cohort <- 5

@@

@@

```{r fig-3b-rank-comparison, include=FALSE,eval=original_plots}
# current_cohort <- 5
colors_plot <- col_df %>%
  filter(method %in% c("C-HP", "C-DCHP")) %>%
  pull(cols)
load(paste(data_path,
  cohort_names[current_cohort],
  "/cohort_hp_stan_result_",
  cohort_names[current_cohort],
  ".RData",
  sep = ""
))
load(paste(data_path,
  cohort_names[current_cohort],
  "/cohort_dchp_stan_result_",
  cohort_names[current_cohort],
  ".RData",
  sep = ""
))
# png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
par(oma = c(0, 0, 2, 0), mar = c(3, 4, 1, 1), mgp = c(0, 0.5, 0))
plot(order(expert_rank_10[[current_cohort]]),
  apply(sim_cohort_hp$f, 2, mean),
  pch = 16, cex = 1.2,
  # col= "steelblue",
  col = colors_plot[1],
  ylab = "", xlab = "",
  xlim = c(1, 12.5), ylim = c(0, 1),
  xaxt = "n", yaxt = "n"
)
segments(order(expert_rank_10[[current_cohort]]),
  apply(sim_cohort_hp$f, 2, mean) -
    apply(sim_cohort_hp$f, 2, sd),
  order(expert_rank_10[[current_cohort]]),
  apply(sim_cohort_hp$f, 2, mean) +
    apply(sim_cohort_hp$f, 2, sd),
  # col= add.alpha("steelblue",0.8),lwd=2)
  col = add.alpha(colors_plot[1], 0.8), lwd = 2
)
points(order(expert_rank_10[[current_cohort]]) + 0.2,
  apply(sim_cohort_dchp$f, 2, mean),
  pch = 16,
  cex = 1.2,
  col = colors_plot[2]
)
# col="goldenrod2")
segments(order(expert_rank_10[[current_cohort]]) + 0.2,
  apply(sim_cohort_dchp$f, 2, mean) - apply(sim_cohort_dchp$f, 2, sd),
  order(expert_rank_10[[current_cohort]]) + 0.2,
  apply(sim_cohort_dchp$f, 2, mean) + apply(sim_cohort_dchp$f, 2, sd),
  col = add.alpha(colors_plot[2], 0.8), lwd = 2
)
# col= add.alpha("goldenrod2",0.8),lwd=2)

@@

```{r, eval=FALSE, include=FALSE}
## need Hmisc for this

@@

Will need to update this with full final simulations.

```{r new-fig-4a, eval = revision_plots}
sim_data_path <- here("output", "revisions", "sim_m3", "june_18", "/")

@@

f_vec <- seq(from = 0.10,
               to = 0.9,
               length.out = num_nodes)

@@

sims_id <- 1:50
sims_id <- sims_id[c(-22,-23, -24, -33, -34, -36, -39, -40, -41, -45)]

for(curr_sim in sims_id) {
  load(paste0(sim_data_path,
              "sim_model3_fit123_",
              curr_sim,
              ".RData"))

@@

  f_m3 <- sim_model3_stan_sim3 %>% select(starts_with("f"))
  m3_ranks <- apply(f_m1, 2, mean)

@@

sim_ranks_mean %>% 
  # filter(model == "C-MMHP") %>% 
  ggplot(aes(node, ranks)) + 
  geom_boxplot() +
  facet_wrap(~model) +
  geom_point(aes(node, true_rank, colour = "red"),
             show.legend = FALSE) +
  labs(title = "Mean rank from each simulation")

@@

true_ranks <- tibble(node = 1:num_nodes, true_rank = f_vec)
true_ranks$node <- factor(true_ranks$node, levels = 1:num_nodes)

sim_ranks %>% 
  ggplot(aes(node, rank)) +
  geom_boxplot() +
  facet_wrap(~model) +
  geom_point(data = true_ranks, aes(node, true_rank, colour = "red"),
             show.legend = FALSE) +
  labs(title = "All Posterior Draws")
```

@@

Need to redo this after finally correctly formulating the 
simulations.

```{r prepare data for 4b,cache=TRUE, eval=revision_plots}
plot.s <- 7 # 7 is pretty good
plot.i <- 4
plot.j <- 5

@@

## then need to load in the state estimate here
load(paste0(here("output", "revisions", "sim_m3"),
  "/", "fit123_state_est_",
  plot.s,
  ".RData"
))

@@

```{r fig-4b-recover-latent-states,fig.width=8,fig.height=4}
mmhp_lty <- 1

@@

```{r actual-plot}
layout(matrix(c(1:6), 6, 1), heights = rep(c(7.5, 2.5), 3))
par(
  mar = c(0, 0.3, 0, 0.1), oma = c(0, 3.5, 4, 0),
  tcl = 0.2, mgp = c(0.5, 0, 0), xpd = TRUE
)

@@

```{r data for fig 5,cache=TRUE}
# load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
# load(paste(sim_data_path,"fit123_state_est.RData",sep=''))
####
#### load new format

@@

## Iteration on 50 simulations
for (s in c(1:n_sim)) {
  load(paste0(sim_data_path, "sim_model3_fit123_", s, ".RData"))
  load(paste(sim_data_path, "fit123_state_est_", s, ".RData", sep = ""))
  clean_sim_data <- cleanSimulationData(
    raw_data = sim_model3_data,
    cut_off = cut_off,
    N = length(object_par$f_vec_1)
  )

@@

  ## model 1
  #########
  model1_par_est <- list(
    lambda0 = mean(sim_model3_stan_sim1$lambda0),
    eta_1 = mean(sim_model3_stan_sim1$eta_1),
    eta_2 = mean(sim_model3_stan_sim1$eta_2),
    eta_3 = mean(sim_model3_stan_sim1$eta_3),
    beta = mean(sim_model3_stan_sim1$beta),

    ### TO DO
    f = apply(sim_model3_stan_sim1$f, 2, mean)
  )

  for (i in c(1:5)) {
    for (j in c(1:5)[-i]) {
      current_t <- sim_model3_data$mmhp_matrix[i, j][[1]]$tau
      m1_object <- list(
        lambda0 = model1_par_est$lambda0,
        alpha = model1_fn$alpha.fun(
          model1_par_est$f[i],
          model1_par_est$f[j],
          model1_par_est$eta_1,
          model1_par_est$eta_2,
          model1_par_est$eta_3
        ),
        beta = model1_par_est$beta
      )
      Lambda_model1_array[s, i, j] <-
        uniHawkesIntegralIntensity(
          object = m1_object,
          events = current_t,
          termination = tail(current_t, 1)
        )
      Lambda_test <- uniHawkesCompensator(
        object = m1_object,
        events = current_t
      )
      KS_model1_array[s, i, j] <- ks.test(Lambda_test, "pexp")$statistic
      KS_p_model1_array[s, i, j] <- ks.test(Lambda_test, "pexp")$p.value
      PR_model1_array[s, i, j] <- uniHawkesPearsonResidual(
        object = m1_object,
        events = current_t,
        termination =
          tail(current_t, 1)
      )
    }
  }

  ## model2
  #############
  model2_par_est <- list(

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.path = "paper_figure/",
  dev = "png", fig.height = 4.5, fig.width = 7,
  warning = FALSE, cache = TRUE
)

@@

```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE, eval=revision_plots}
# current_cohort <- 5
current_cohort <- 5

@@

ks.stat.matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
ks_pval_chp <- matrix(0, nrow = mice_number, ncol = mice_number)
n_matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
Lambda_matrix <- matrix(list(), nrow = mice_number, ncol = mice_number)
for (k in 1:mice_number) {
  for (l in c(1:mice_number)[-k]) {
    i <- expert_rank_10[[current_cohort]][k]
    j <- expert_rank_10[[current_cohort]][l]
    pair <- which(unique_pairs_df$initiator == i & 
                    unique_pairs_df$recipient == j)
    if (length(pair) > 0) {
      param_mean <- list(
        lambda0 = mean(sim_cohort_hp$lambda0),
        alpha = model1_fn$alpha.fun(
          f_est[i],
          f_est[j],
          eta1_mean,
          eta2_mean,
          eta3_mean
        ),
        beta = mean(sim_cohort_hp$beta)
      )
      current_window_vec <- unique_pairs_df$observe[[pair]]
      all_Lambda <- numeric(0)
      for (cur in c(1:length(current_window_vec))) { ## check length > 2
        cur_win <- current_window_vec[cur]
        current_event_time <- return_df[return_df$initiator == i &
          return_df$recipient == j &
          return_df$observe.id == cur_win, "event.times"][[1]]
        current_obs_time <- return_df[return_df$initiator == i &
          return_df$recipient == j &
          return_df$observe.id == cur_win, "observe.time"]
        Lambda_vec <- uniHawkesCompensator(
          object = param_mean,
          events = c(
            current_event_time,
            current_obs_time
          )
        )
        all_Lambda <- c(all_Lambda, Lambda_vec)
        n_matrix[i, j] <- n_matrix[i, j] + length(current_event_time)
      }
      if (length(all_Lambda) > 0) {
        ks.stat.matrix[i, j] <- ks.test(all_Lambda, "pexp",
          rate = 1 / mean(all_Lambda)
        )$statistic
        ks_pval_chp[i, j] <- ks.test(all_Lambda, "pexp",
          rate = 1 / mean(all_Lambda)
        )$p.value
        Lambda_matrix[i, j][[1]] <- all_Lambda
      }
    }
  }
}
#
# png(paste(plot_path,
#           "/diagonsis_model1_",
#           cohort_names[current_cohort],
#           ".png",
#           sep = ''),
#     width=480,height=480)
# -------------- KS plot (stat)
col.vec <- cRamp(as.vector(ks.stat.matrix))
# need to do some sort of transformation between these here
vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix))))
# order(as.vector(ks.stat.matrix),method = "")

@@

mtext(
  text = expert_rank_10[[current_cohort]],
  side = 1, line = 1.8, outer = TRUE, cex = 1.8,
  at = 1 / 14 * c(1:12) - 1 / 22
)
mtext(
  text = expert_rank_10[[current_cohort]],
  side = 2, line = 0.5, outer = TRUE, cex = 1.8,
  at = 1 / 12 * c(12:1) - 1 / 20, las = 2
)
mtext(
  text = "(b)", side = 3, line = 1.4, outer = TRUE,
  cex = 2.2,
  at = 0.45, font = 2
)
# dev.off()
ks_chp <- ks.stat.matrix

@@

```{r fig-3a-baseline-rate, eval=revision_plots}
current_cohort <- 5
# current_cohort <- 6 # 3 is maybe ok, 6/7 is interesting

@@

## New Fig

KS Plot for C-DCHP

```{r ks-c-dchp, eval=FALSE, warning=FALSE}
ks.stat.matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
ks_pval_dchp <- matrix(0, ncol = mice_number, nrow = mice_number)
n_matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
Lambda_matrix <- matrix(list(), nrow = mice_number, ncol = mice_number)

gamma_mean <- apply(sim_cohort_dchp$gamma, 2, mean)
zeta_mean <- apply(sim_cohort_dchp$zeta, 2, mean)
eta1_mean <- mean(sim_cohort_dchp$eta_1)
eta2_mean <- mean(sim_cohort_dchp$eta_2)
eta3_mean <- mean(sim_cohort_dchp$eta_3)

for (k in 1:mice_number) {
  for (l in c(1:mice_number)[-k]) {
    i <- expert_rank_10[[current_cohort]][k]
    j <- expert_rank_10[[current_cohort]][l]
    pair <- which(unique_pairs_df$initiator == i & 
                    unique_pairs_df$recipient == j)
    if (length(pair) > 0) {
      param_mean <- list(
        lambda0 = gamma_mean[i] + zeta_mean[j],
        ## need to modify this
        # lambda0 <- mean(sim_cohort_dchp$gamma)
        alpha = model1_fn$alpha.fun(
          f_est[i],
          f_est[j],
          eta1_mean,
          eta2_mean,
          eta3_mean
        ),
        beta = mean(sim_cohort_dchp$beta)
      )
      current_window_vec <- unique_pairs_df$observe[[pair]]
      all_Lambda <- numeric(0)
      for (cur in c(1:length(current_window_vec))) { ## check length > 2
        cur_win <- current_window_vec[cur]
        current_event_time <- return_df[return_df$initiator == i &
          return_df$recipient == j &
          return_df$observe.id == cur_win, "event.times"][[1]]
        current_obs_time <- return_df[return_df$initiator == i &
          return_df$recipient == j &
          return_df$observe.id == cur_win, "observe.time"]
        Lambda_vec <- uniHawkesCompensator(
          object = param_mean,
          events = c(
            current_event_time,
            current_obs_time
          )
        )
        all_Lambda <- c(all_Lambda, Lambda_vec)
        n_matrix[i, j] <- n_matrix[i, j] + length(current_event_time)
      }
      if (length(all_Lambda) > 0) {
        ks.stat.matrix[i, j] <- ks.test(all_Lambda, "pexp",
          rate = 1 / mean(all_Lambda)
        )$statistic
        ks_pval_dchp[i, j] <- ks.test(all_Lambda, "pexp",
          rate = 1 / mean(all_Lambda)
        )$p.value
        Lambda_matrix[i, j][[1]] <- all_Lambda
      }
    }
  }
}
col.vec <- cRamp(as.vector(ks.stat.matrix))
# need to do some sort of transformation between these here
vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix))))
# order(as.vector(ks.stat.matrix),method = "")

temp <- cLegend(as.vector(ks.stat.matrix))
image(1, col_obj$x.vec,
  matrix(
    data = col_obj$x.vec,
    ncol = length(col_obj$x.vec), nrow = 1
  ),
  col = col_obj$col.vec,
  xlab = "", ylab = "", axes = FALSE
)
axis(4,
  at = c(0, 0.3, 0.6), labels = c(0, 0.3, 0.6), las = HORIZONTAL <- 1,
  cex.axis = 2.4
)

mtext(
  text = expert_rank_10[[current_cohort]],
  side = 1, line = 1.8, outer = TRUE, cex = 1.8,
  at = 1 / 14 * c(1:12) - 1 / 22
)
mtext(
  text = expert_rank_10[[current_cohort]],
  side = 2, line = 0.5, outer = TRUE, cex = 1.8,
  at = 1 / 12 * c(12:1) - 1 / 20, las = 2
)
mtext(
  text = "C-DCHP", side = 3, line = 1.4, outer = TRUE,
  cex = 2.2,
  at = 0.45, font = 2
)
# dev.off()

ks_dchp <- ks.stat.matrix

Plot the negative log of the p values here.

```{r potential-fig3-diag, eval=FALSE}
M1_ks_p <- tibble(ks_p = as.vector(ks_chp), method = "C-HP")

M2_ks_p <- tibble(ks_p = as.vector(ks_dchp), 
                  method = "C-DCHP")

ks_p <- bind_rows(M1_ks_p, M2_ks_p) %>% 
  left_join(col_df, by = "method")

cols_plot <- col_df %>%
  filter(method %in% c("C-HP", "C-DCHP")) %>% 
  pull(cols)

exp_fcn <- function(x) exp(-x)

ks_p$method <- factor(ks_p$method, levels = c("C-HP", "C-DCHP"))

ks_p %>% 
  filter(ks_p != 0) %>% 
  mutate(log_p = -log(ks_p)) %>% 
  ggplot(aes(x = log_p)) + 
  # geom_freqpoly(binwidth = 20) +
  geom_histogram(aes(y = ..density.., fill = method), bins = 50) +
  scale_fill_manual(values = cols_plot) +
  labs(y = "Negative Log KS Statistic P Value") +
  stat_function(fun = exp_fcn, colour = "red") +
  facet_wrap(~method) +
  labs(fill = "Method") +
  theme_minimal()

Could repeat this across all cohorts?

```{r above across all_cohorts, eval=FALSE}

ks_chp_array <- array(0, dim = c(10, mice_number, mice_number))
ks_dchp_array <- array(0, dim = c(10, mice_number, mice_number))

for(current_cohort in 1:10) {
  load(paste(data_path, cohort_names[current_cohort],
    "/cohort_hp_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
    "/cohort_dchp_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  eta1_mean <- mean(sim_cohort_hp$eta_1)
  eta2_mean <- mean(sim_cohort_hp$eta_2)
  eta3_mean <- mean(sim_cohort_hp$eta_3)
  f_est <- apply(sim_cohort_hp$f, 2, mean)
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  return_df <- cleanObservationPeriod(current_cohort,
    raw_df =
      full_data[[cohort_names[current_cohort]]],
    clean_data
  )
  unique_pairs_df <- return_df %>%
    group_by(initiator, recipient) %>%
    dplyr::summarize(
      count = n(),
      observe = list(observe.id),
      observe.length = list(observe.time),
      no.events = list(no.events)
    )
  unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")])

  ks.stat.matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
  ks_pval_chp <- matrix(0, nrow = mice_number, ncol = mice_number)
  n_matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
  Lambda_matrix <- matrix(list(), nrow = mice_number, ncol = mice_number)
  for (k in 1:mice_number) {
    for (l in c(1:mice_number)[-k]) {
      i <- expert_rank_10[[current_cohort]][k]
      j <- expert_rank_10[[current_cohort]][l]
      pair <- which(unique_pairs_df$initiator == i & 
                      unique_pairs_df$recipient == j)
      if (length(pair) > 0) {
        param_mean <- list(
          lambda0 = mean(sim_cohort_hp$lambda0),
          alpha = model1_fn$alpha.fun(
            f_est[i],
            f_est[j],
            eta1_mean,
            eta2_mean,
            eta3_mean
          ),
          beta = mean(sim_cohort_hp$beta)
        )
        current_window_vec <- unique_pairs_df$observe[[pair]]
        all_Lambda <- numeric(0)
        for (cur in c(1:length(current_window_vec))) { ## check length > 2
          cur_win <- current_window_vec[cur]
          current_event_time <- return_df[return_df$initiator == i &
            return_df$recipient == j &
            return_df$observe.id == cur_win, "event.times"][[1]]
          current_obs_time <- return_df[return_df$initiator == i &
            return_df$recipient == j &
            return_df$observe.id == cur_win, "observe.time"]
          Lambda_vec <- uniHawkesCompensator(
            object = param_mean,
            events = c(
              current_event_time,
              current_obs_time
            )
          )
          all_Lambda <- c(all_Lambda, Lambda_vec)
          n_matrix[i, j] <- n_matrix[i, j] + length(current_event_time)
        }
        if (length(all_Lambda) > 0) {
          ks.stat.matrix[i, j] <- ks.test(all_Lambda, "pexp",
            rate = 1 / mean(all_Lambda)
          )$statistic
          ks_chp_array[current_cohort, i, j] <- ks.test(all_Lambda,
                                                        "pexp",
            rate = 1 / mean(all_Lambda)
          )$p.value
          Lambda_matrix[i, j][[1]] <- all_Lambda
        }
      }
    }
  }

  ### c-dchp
  gamma_mean <- apply(sim_cohort_dchp$gamma, 2, mean)
  zeta_mean <- apply(sim_cohort_dchp$zeta, 2, mean)
  eta1_mean <- mean(sim_cohort_dchp$eta_1)
  eta2_mean <- mean(sim_cohort_dchp$eta_2)
  eta3_mean <- mean(sim_cohort_dchp$eta_3)

  for (k in 1:mice_number) {
    for (l in c(1:mice_number)[-k]) {
      i <- expert_rank_10[[current_cohort]][k]
      j <- expert_rank_10[[current_cohort]][l]
      pair <- which(unique_pairs_df$initiator == i & 
                      unique_pairs_df$recipient == j)
      if (length(pair) > 0) {
        param_mean <- list(
          lambda0 = gamma_mean[i] + zeta_mean[j],
          ## need to modify this
          # lambda0 <- mean(sim_cohort_dchp$gamma)
          alpha = model1_fn$alpha.fun(
            f_est[i],
            f_est[j],
            eta1_mean,
            eta2_mean,
            eta3_mean
          ),
          beta = mean(sim_cohort_dchp$beta)
        )
        current_window_vec <- unique_pairs_df$observe[[pair]]
        all_Lambda <- numeric(0)
        for (cur in c(1:length(current_window_vec))) { ## check length > 2
          cur_win <- current_window_vec[cur]
          current_event_time <- return_df[return_df$initiator == i &
            return_df$recipient == j &
            return_df$observe.id == cur_win, "event.times"][[1]]
          current_obs_time <- return_df[return_df$initiator == i &
            return_df$recipient == j &
            return_df$observe.id == cur_win, "observe.time"]
          Lambda_vec <- uniHawkesCompensator(
            object = param_mean,
            events = c(
              current_event_time,
              current_obs_time
            )
          )
          all_Lambda <- c(all_Lambda, Lambda_vec)
          n_matrix[i, j] <- n_matrix[i, j] + length(current_event_time)
        }
        if (length(all_Lambda) > 0) {
          ks.stat.matrix[i, j] <- ks.test(all_Lambda, "pexp",
            rate = 1 / mean(all_Lambda)
          )$statistic
          ks_dchp_array[current_cohort, i, j] <- ks.test(all_Lambda, "pexp",
            rate = 1 / mean(all_Lambda)
          )$p.value
          Lambda_matrix[i, j][[1]] <- all_Lambda
        }
      }
    }
  }
}

```{r plot-all-cohorts, eval=FALSE}
M1_ks_p <- tibble(ks_p = as.vector(ks_chp_array), method = "C-HP")

M2_ks_p <- tibble(ks_p = as.vector(ks_dchp_array), 
                  method = "C-DCHP")

ks_p <- bind_rows(M1_ks_p, M2_ks_p) %>% 
  left_join(col_df, by = "method")

cols_plot <- col_df %>%
  filter(method %in% c("C-HP", "C-DCHP")) %>% 
  pull(cols)

exp_fcn <- function(x) exp(-x)

ks_p$method <- factor(ks_p$method, levels = c("C-HP", "C-DCHP"))

ks_p %>% 
  filter(ks_p != 0) %>% 
  mutate(log_p = -log(ks_p)) %>% 
  ggplot(aes(x = log_p)) + 
  # geom_freqpoly(binwidth = 20) +
  geom_histogram(aes(y = ..density.., fill = method), bins = 50) +
  scale_fill_manual(values = cols_plot) +
  labs(y = "Negative Log KS Statistic P Value") +
  stat_function(fun = exp_fcn, colour = "red") +
  facet_wrap(~method) +
  labs(fill = "Method") +
  theme_minimal()

@@

```{r fig-3b-rank-comparison, include=FALSE,eval=original_plots}
current_cohort <- 5
colors_plot <- col_df %>%
  filter(method %in% c("C-HP", "C-DCHP")) %>%
  pull(cols)
load(paste(data_path,
  cohort_names[current_cohort],
  "/cohort_hp_stan_result_",
  cohort_names[current_cohort],
  ".RData",
  sep = ""
))
load(paste(data_path,
  cohort_names[current_cohort],
  "/cohort_dchp_stan_result_",
  cohort_names[current_cohort],
  ".RData",
  sep = ""
))
# png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
par(oma = c(0, 0, 2, 0), mar = c(3, 4, 1, 1), mgp = c(0, 0.5, 0))
plot(order(expert_rank_10[[current_cohort]]),
  apply(sim_cohort_hp$f, 2, mean),
  pch = 16, cex = 1.2,
  # col= "steelblue",
  col = colors_plot[1],
  ylab = "", xlab = "",
  xlim = c(1, 12.5), ylim = c(0, 1),
  xaxt = "n", yaxt = "n"
)
segments(order(expert_rank_10[[current_cohort]]),
  apply(sim_cohort_hp$f, 2, mean) -
    apply(sim_cohort_hp$f, 2, sd),
  order(expert_rank_10[[current_cohort]]),
  apply(sim_cohort_hp$f, 2, mean) +
    apply(sim_cohort_hp$f, 2, sd),
  # col= add.alpha("steelblue",0.8),lwd=2)
  col = add.alpha(colors_plot[1], 0.8), lwd = 2
)
points(order(expert_rank_10[[current_cohort]]) + 0.2,
  apply(sim_cohort_dchp$f, 2, mean),
  pch = 16,
  cex = 1.2,
  col = colors_plot[2]
)
# col="goldenrod2")
segments(order(expert_rank_10[[current_cohort]]) + 0.2,
  apply(sim_cohort_dchp$f, 2, mean) - apply(sim_cohort_dchp$f, 2, sd),
  order(expert_rank_10[[current_cohort]]) + 0.2,
  apply(sim_cohort_dchp$f, 2, mean) + apply(sim_cohort_dchp$f, 2, sd),
  col = add.alpha(colors_plot[2], 0.8), lwd = 2
)
# col= add.alpha("goldenrod2",0.8),lwd=2)

@@

```{r, eval=FALSE, include=FALSE}
## need Hmisc for this
library(Hmisc)

@@

Will need to update this with full final simulations but fully set up now.

```{r new-fig-4a, eval = revision_plots}
sim_data_path <- here("output", "revisions", "sim_m3", "sim_3", "/")

@@

f_vec <- seq(from = 0.2,
               to = 0.9,
               length.out = num_nodes)

@@

sims <- 1:20
sims <- sims[c(-9, -13)]

for(curr_sim in sims) {
  load(paste0(sim_data_path,
              "sim_model3_fit123_",
              curr_sim,
              ".RData"))

@@

  f_m3 <- sim_model3_stan_sim3 %>% select(starts_with("f"))
  m3_ranks <- apply(f_m3, 2, mean)

@@

sim_ranks_mean$model <- factor(sim_ranks_mean$model, 
                               levels = c( "C-HP", "C-DCHP", "C-MMHP"))

mean_sims <- sim_ranks_mean %>% 
  left_join(col_df, by = c("model" = "method"))

mean_sims$model <- factor(mean_sims$model, levels = c("C-HP", "C-DCHP",
                                                      "C-MMHP"))

true_ranks <- tibble(node = rep(1:num_nodes,3),
                     true_rank = rep(f_vec,3),
                     model = c(rep("C-HP", 10),rep("C-DCHP", 10),
                               rep("C-MMHP", 10)))
true_ranks$node <- factor(true_ranks$node, levels = 1:num_nodes)

true_ranks$model <- factor(true_ranks$model, 
                           levels = c("C-HP", "C-DCHP","C-MMHP"))

mean_sims %>% 
  # filter(model == "C-MMHP") %>% 
  ggplot(aes(node, ranks, fill = model)) + 
  geom_boxplot(show.legend = FALSE) +
  scale_fill_manual(values = model_colors, guide = FALSE) +
  # geom_point(aes(node, true_rank, colour = "red")) +
  ylim(c(0,1)) +
  labs(title = "(a)",
       subtitle = "Mean rank from each simulation", 
       y = "Posterior Mean Rank", x = "Node") +
  facet_wrap(~model) +
  geom_point(data = true_ranks,
             aes(node, true_rank, colour = "True Value")) +
  scale_shape_discrete(name = "True Value") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5, size = 26),
        text = element_text(size = 18),
        legend.text = element_text(size = 18))

@@

# sim_ranks %>%
#   ggplot(aes(node, rank)) +
#   geom_boxplot() +
#   facet_wrap(~model) +
#   geom_point(data = true_ranks, aes(node, true_rank, colour = "red"),
#              show.legend = FALSE) +
#   labs(title = "All Posterior Draws")
```

@@

Need to modify this after finally correctly formulating the 
simulations.

```{r prepare data for 4b,cache=TRUE, eval=FALSE}
plot.s <- 7 # 7 is pretty good
plot.i <- 4
plot.j <- 5

@@

## then need to load in the state estimate here
# load(paste0(here("output", "revisions", "sim_m3"),
#   "/", "fit123_state_est_",
#   plot.s,
#   ".RData"
# ))

load(paste0(
  sim_data_path, "/", "fit123_state_est_",
  plot.s,
  ".RData"
))

state.est.latent.mmhp <- interpolate_state_est_lst[plot.i, plot.j][[1]]
state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
  termination = 50 
  ### TO DO update for longer sims
)

@@

```{r fig-4b-recover-latent-states,fig.width=8,fig.height=4, eval=FALSE}
mmhp_lty <- 1

@@

```{r actual-plot, eval=FALSE}
layout(matrix(c(1:6), 6, 1), heights = rep(c(7.5, 2.5), 3))
par(
  mar = c(0, 0.3, 0, 0.1), oma = c(0, 3.5, 4, 0),
  tcl = 0.2, mgp = c(0.5, 0, 0), xpd = TRUE
)

@@

```{r data for fig 5,cache=TRUE, eval=revision_plots}
n_sim <- 25

object_par <- list(f_vec_1 = seq(from = 0.1, to = 0.9,
                                 length.out = num_nodes))
### TO DO

@@

## Iteration on 50 simulations
sims <- 1:25
sims <- sims[c(-12, -22, -23, -24)]

for (s in sims) {
  print(s)
  load(paste0(sim_data_path, "sim_model3_fit123_", s, ".RData"))
  load(paste(sim_data_path, "fit123_state_est_", s, ".RData", sep = ""))
  clean_sim_data <- cleanSimulationData(
    raw_data = sim_model3_data,
    cut_off = cut_off,
    N = length(object_par$f_vec_1)
  )

@@

  ## model 1
  #########
  ### transform from cmdstan here
  f_draws <- sim_model3_stan_sim1 %>% 
  select(starts_with("f"))

  ###
  model1_par_est <- list(
    lambda0 = mean(sim_model3_stan_sim1$lambda0),
    eta_1 = mean(sim_model3_stan_sim1$eta_1),
    eta_2 = mean(sim_model3_stan_sim1$eta_2),
    eta_3 = mean(sim_model3_stan_sim1$eta_3),
    beta = mean(sim_model3_stan_sim1$beta),
    f = apply(f_draws, 2, mean)
  )

  for (i in c(1:num_nodes)) {
    for (j in c(1:num_nodes)[-i]) {
      current_t <- sim_model3_data$mmhp_matrix[i, j][[1]]$tau
      m1_object <- list(
        lambda0 = model1_par_est$lambda0,
        alpha = model1_fn$alpha.fun(
          model1_par_est$f[i],
          model1_par_est$f[j],
          model1_par_est$eta_1,
          model1_par_est$eta_2,
          model1_par_est$eta_3
        ),
        beta = model1_par_est$beta
      )
      Lambda_model1_array[s, i, j] <-
        uniHawkesIntegralIntensity(
          object = m1_object,
          events = current_t,
          termination = tail(current_t, 1)
        )
      Lambda_test <- uniHawkesCompensator(
        object = m1_object,
        events = current_t
      )
      KS_model1_array[s, i, j] <- ks.test(Lambda_test, "pexp")$statistic
      KS_p_model1_array[s, i, j] <- ks.test(Lambda_test, "pexp")$p.value
      PR_model1_array[s, i, j] <- uniHawkesPearsonResidual(
        object = m1_object,
        events = current_t,
        termination =
          tail(current_t, 1)
      )
    }
  }

  ## model2
  #############
  ### convert to cmdstan
  gamma_draws <- sim_model3_stan_sim2 %>% 
  select(starts_with("gamma"))
  zeta_draws <- sim_model3_stan_sim2 %>% 
  select(starts_with("zeta"))
  f_draws <- sim_model3_stan_sim2 %>% 
  select(starts_with("f"))
